Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-19 ICLR25/relatedwork.tex

Hybrid MILP can be seen as a refinement of $\alpha,\beta$-Crown~\cite{crown}, though its refined accurate path is vastly different than the base Branch and Bound technique used in 
$\alpha,\beta$ CROWN, BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete}, which call BaB once per output neuron. In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities. In simple networks, like those trained robustly, branch and bound is highly efficient, focusing on branches crucial for verifying the actual property. However, branch and bound hits a complexity barrier when verifying harder instances, due to an overwhelming number of branches, as displayed in Table \ref{table_beta}. This is not the csae of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.
That shortcoming was already witnessed in \cite{crown}, and
a very specific solution

@@

For verification-agnostic DNNs that are not too large,  $\beta$-CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding. In {\CMP}, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength. As it is more efficient, we compute bounds for neurons in {\em all} the layers. This would be infeasible without the selection based on the compensation. The refined version of $\beta$-CROWN is particularly accurate on small DNNs. As the depth grows, the more work is left to BaB and \CMP is more accurate (Table \ref{tab:example}).

Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, ($\alpha$)($\beta$)-CROWN)\cite{prima,crown}, Hybrid MILP. These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances as shown in Table \ref{table_complete}.

>>>>

Hybrid MILP can be seen as a refinement of $\alpha,\beta$-Crown~\cite{crown}, though its refined accurate path is vastly different than the base Branch and Bound technique used in 
$\alpha,\beta$ CROWN, BaBSR \cite{BaB} and MN-BaB \cite{ferrari2022complete}, which call BaB once per output neuron. In the worst case, this involves considering all possible ReLU configurations, though branch and bound typically circumvents most possibilities. In simple networks, like those trained robustly, branch and bound is highly efficient, focusing on branches crucial for verifying the actual property. However, branch and bound hits a complexity barrier when verifying harder instances, due to an overwhelming number of branches, as displayed in Table \ref{table_beta}. This is not the csae of Hybrid MILP, see Table \ref{table_hybrid}, which is much more accurate than $\alpha,\beta$-Crown.
That shortcoming for hard instances was witnessed in \cite{crown}, and a very specific solution using the full MILP encoding for the first few layers of a DNN was drafted, following similar proposal \cite{MILP2}. There are two key issues with this techniques: it is slow, as every neurons up to the layer are encoded using an integer variable, and it cannot scale to DNN with many neurons, making it not that accurate for intermediate networks (e.g. 9x100,9x200, Table \ref{table_hybrid}), and not usable for larger DNNs (6x500, CNN-B-Adv), whereas Hybrid MILP does scale.

@@

%For verification-agnostic DNNs that are not too large,  $\beta$-CROWN (and PRIMA) resorts to a {\em refined} path \cite{MILP2}, where the bounds {\em on the first few layers} are refined using an exact MILP encoding. In {\CMP}, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength. As it is more efficient, we compute bounds for neurons in {\em all} the layers. This would be infeasible without the selection based on the compensation. The refined version of $\beta$-CROWN is particularly accurate on small DNNs. As the depth grows, the more work is left to BaB and \CMP is more accurate (Table \ref{tab:example}).

Finally, methods such as Reluplex / Marabou \cite{Reluplex,katz2019marabou}  abstract the network: they diverge significantly from those abstracting values such as PRIMA, $\alpha,\beta$-CROWN)\cite{prima,crown}, Hybrid MILP. 
These network-abstraction algorithms are designed to be {\em complete} but completeness comes at the price of significant scalability challenges, and in practice they time-out on hard instances as shown in Table \ref{table_complete}.
